---
title: "ICA 9.16"
format: html
---

# Import data
```{r}
# Import data
hikes <- read.csv("https://mac-stat.github.io/data/high_peaks.csv")
head(hikes)
```
a.What features would we like a visualization of the categorical difficulty rating variable to capture? 
Answer: bar plot
b.What about a visualization of the quantitative elevation variable?
Answer: histogram

Exercise 2: Load tidyverse
We’ll address the above questions using ggplot tools. Try running the following chunk and simply take note of the error message – this is one you’ll get a lot!
```{r}
# Use the ggplot function
# Load the package
library(tidyverse)
ggplot(hikes, aes(x = rating))
```
Exercise 3: Bar Chart of Ratings - Part 1
Consider some specific research questions about the difficulty rating of the hikes:

How many hikes fall into each category?
Are the hikes evenly distributed among these categories, or are some more common than others?
All of these questions can be answered with: (1) a bar chart; of (2) the categorical data recorded in the rating column. First, set up the plotting frame:

```{r}
ggplot(hikes, aes(x = rating)) 
```
Think about:

What did this do? What do you observe?
Answer: create the frame for the plot.
What, in general, is the first argument of the ggplot() function?
Answer: numbers of Hikes
What is the purpose of writing x = rating?
Answer: setting the rating as the independent variable.
What do you think aes stands for?!?
Answer：Aesthetics

Exercise 4: Bar Chart of Ratings - Part 2
Now let’s add a geometric layer to the frame / canvas, and start customizing the plot’s theme. To this end, try each chunk below, one by one. In each chunk, make a comment about how both the code and the corresponding plot both changed.
NOTE:
	•	Pay attention to the general code properties and structure, not memorization.
	•	Not all of these are “good” plots. We’re just exploring ggplot.
```{r}
# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar()
# the graph is now set as a bar plot while setting rating as independent variable.
```
```{r}
# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar() +
  labs(x = "Rating", y = "Number of hikes")
# there is label corresponding to each variable (each variable is given by a name)
```

```{r}
# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar(fill = "blue") +
  labs(x = "Rating", y = "Number of hikes")
# The graph is colored by blue
```
```{r}
# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue") +
  labs(x = "Rating", y = "Number of hikes")
# the edges of the blue bars is colored by orange
```
	
```{r}
# COMMENT on the change in the code and the corresponding change in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue")  +
  labs(x = "Rating", y = "Number of hikes") +
  theme_minimal()
#the color of the backgournd is changed.
```
Exercise 5: Bar Chart Follow-up
Part a
Reflect on the ggplot() code.

What’s the purpose of the +? When do we use it?
Answer: It is used to continue adding conditions
We added the bars using geom_bar()? Why “geom”?
Answer: because bar is the format which is included in geom.
What does labs() stand for?
Answer: it stands for label.
What’s the difference between color and fill?
Answer: color is for the edges and fill is about the inside the bar.
Part b
In general, bar charts allow us to examine the following properties of a categorical variable:

observed categories: What categories did we observe?
Answer: the hikes are mainly moderate, only few of them are difficult
variability between categories: Are observations evenly spread out among the categories, or are some categories more common than others?
We must then translate this information into the context of our analysis, here hikes in the Adirondacks. Summarize below what you learned from the bar chart, in context.

Part c
Is there anything you don’t like about this barplot? For example: check out the x-axis again.

Answer: the ratings should be ranged from easy to difficult.

Exercise 6: Sad Bar Chart
Let’s now consider some research questions related to the quantitative elevation variable:

Among the hikes, what’s the range of elevation and how are the hikes distributed within this range (eg, evenly, in clumps, “normally”)?
What’s a typical elevation?
Are there any outliers, ie, hikes that have unusually high or low elevations?
Here:

Construct a bar chart of the quantitative elevation variable.
Explain why this might not be an effective visualization for this and other quantitative variables. (What questions does / doesn’t it help answer?)
```{r}
ggplot(hikes, aes(x = elevation)) + 
  geom_bar()
#the outcomes related to elevation are various so it looks really chaotic.
```
Exercise 7: A Histogram of Elevation
Quantitative variables require different viz than categorical variables. Especially when there are many possible outcomes of the quantitative variable. It’s typically insufficient to simply count up the number of times we’ve observed a particular outcome as the bar graph did above. It gives us a sense of ranges and typical outcomes, but not a good sense of how the observations are distributed across this range. We’ll explore two methods for graphing quantitative variables: histograms and density plots.

Histograms are constructed by (1) dividing up the observed range of the variable into ‘bins’ of equal width; and (2) counting up the number of cases that fall into each bin. Check out the example below:



Part a
Let’s dig into some details.

How many hikes have an elevation between 4500 and 4700 feet?
Answer:6
How many total hikes have an elevation of at least 5100 feet?
Answer:2
Part b
Now the bigger picture. In general, histograms allow us to examine the following properties of a quantitative variable:

typical outcome: Where’s the center of the data points? What’s typical?
variability & range: How spread out are the outcomes? What are the max and min outcomes?
shape: How are values distributed along the observed range? Is the distribution symmetric, right-skewed, left-skewed, bi-modal, or uniform (flat)?
outliers: Are there any outliers, ie, outcomes that are unusually large/small?
We must then translate this information into the context of our analysis, here hikes in the Adirondacks. Addressing each of the features in the above list, summarize below what you learned from the histogram, in context.

Answer:the elevation is ranged from 3700 to 5500 feet, and it is distributed centrally arround 4500.
